---
title: "workstation"
author: "RF"
---




```{r}
library(ggplot2)
library(dplyr)
library(mizerEvolution)
```




```{r}
params <- evoParams(no_sp =  5)

sim <- project(params)

plotBiomass(sim)

plotDiet(sim@params, species = "5")

simEvo <- evoProject(params = params, t_max = 200, mutation = 3, trait = "beta")

plotDynamics(simEvo)

plotevoTrait(simEvo, traitID = "beta", returnData = F)

```


### Notes

for creating new traits, the specific cases are not working. for now any trait in species_params can be randomly changed but it doesnt change any calculations around the parameter / trait
need to rewrite the cases to remove all the useless stuff

getSMort to calculate starvation is missing, check mizer or some old files. Maybe mizer does it better anyway

not sure feeding level through time works well, probably useless anyway, need to remove it

# todo


improve readme invasion section

function update evo so can convert NS params and play with it

## invasions

```{r}

params <- evoParams(no_sp =  5)

simEvo <- evoProject(params = params, t_max = 100, alien = 3, mutation = 0)

```

